---
title: "Project Proposal"
author: "Conquerors"
date: "`r Sys.Date()`"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(readr)
```

## 1. Introduction

Fundamental Question: Which variables (or combinations of these) are the most important indicators when determining whether an individual will subscribe to a term deposit?

Data:
Where it came from?
How it was collected?
What are the cases?
What are the variables

The dataset "Banking Dataset - Marketing Targets" by Prakhar Rathi contains data  from a direct marketing campaign by a Portuguese Banking Institution. Clients were contacted by phone calls in order to collect the data.There are 45,211 cases with 17 variables;labelled: age, job, marital, education, default, balance, housing, loan, contact, day, month, duration, campaign, pdays, previous, poutcome, y.

## 2. Data

```{r import-data}

banking <- read_delim("/cloud/project/data/Banking Dataset.csv",
            delim = ";", escape_double = FALSE, trim_ws = TRUE)

glimpse(banking)

```


## 3. Data analysis plan



