---
title: "Project Proposal"
author: "Conquerors"
date: "`r Sys.Date()`"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(readr)
```

## 1. Introduction

Fundamental Question: Which variables (or combinations of these) are the most important indicators when determining whether an individual will subscribe to a term deposit?

Data:
Where it came from?
The dataset "Banking Dataset - Marketing Targets" by Prakhar Rathi contains data  from a direct marketing campaign by a Portuguese Banking Institution.

How it was collected?
Clients were contacted by phone calls in order to collect the data.


What are the cases?
There are 45,211 cases with 17 variables


What are the variables
variables;labelled: age, job, marital, education, default, balance, housing, loan, contact, day, month, duration, campaign, pdays, previous, poutcome, y.

The dataset "Banking Dataset - Marketing Targets" by Prakhar Rathi contains data  from a direct marketing campaign by a Portuguese Banking Institution. Clients were contacted by phone calls in order to collect the data.There are 45,211 cases with 17 variables;labelled: age, job, marital, education, default, balance, housing, loan, contact, day, month, duration, campaign, pdays, previous, poutcome, y.

## 2. Data

```{r import-data}

banking <- read_delim("/cloud/project/data/Banking Dataset.csv",
            delim = ";", escape_double = FALSE, trim_ws = TRUE)

glimpse(banking)

```


## 3. Data analysis plan

The outcome of this data (Y) is whether or not the client has subscribed to the term deposit the bank is offering. The predictor(X) variables are all the other variables in the data set excluding Y which is the outcome variable. Our question will be answered by determining which of these variables are better predictors for this outcome.

We are not using any comparison groups because our data analysis research question is not based on experiment testing but rather on analyzing causation between different sets of variables that have all been pre-recorded.

**Preliminary Data Analysis:**

This first metric is used to observe the overall success of the bank marketing campaign.
```{r Example }
banking %>%
  mutate(y=fct_recode(y, Subscribed= "yes", `Not Subscribed` = "no")) %>%
ggplot(aes(y = y,fill= y)) +
  geom_bar() +
  guides(fill = "none") +
  scale_fill_manual(values = c("Subscribed"="#3b9e37", "Not Subscribed"="#d91a1a")) +
   labs(
    x = NULL,
    y = NULL,
    title = "Number of clients that subscribed to a term deposit",
  )
```

Could the client's jobs have an impact on whether they subscribe to term deposits?
```{r Example stats}
banking %>%
mutate(
  job= fct_recode(job, Administrative = "admin.", Management = "management", Entrepreneur= "entrepreneur", `Blue Collar` = "blue-collar", Housemaid = "housemaid", Technician = "technician" , Services = "services", Student = "student" , `Self Employed`= "self-employed", Unemployed = "unemployed", Unknown= "unknown", Retred = "retired" ),
  y=fct_recode(y, Subscribed= "yes", `Not Subscribed` = "no")) %>%
ggplot(aes(y = y,fill= y)) +
  geom_bar() +
  guides(fill = "none") +
  scale_fill_manual(values = c("Subscribed"="#3b9e37", "Not Subscribed"="#d91a1a")) +
  facet_wrap(.~job, scales = "free_x") +
  labs(
    x = NULL,
    y = NULL,
    title = "Number of clients that subscribed to a term deposit",
    subtitle= "Faceted by jobs"
    
  )
```

Comparing two continuous variables such as Bank Balance and Duration of Call could help us determine whether the bank's marketing campaign placed more emphasis on clients with very large balances or negative ones (clients in need or with dept). Perhaps more effort was given to these groups of clients?

```{r Example plot}
banking %>%
  group_by(contact)%>%
  summarize(balance,duration)%>%
  ggplot(aes(x=balance,y=duration,color= contact)) +
  geom_smooth() +
  guides(color = "none") +
  facet_wrap(~contact,nrow = 3, scales = "free_x")+
labs(
  title= "Relationship between balance and duration of call",
  x= "Average Yearly Bank Balance (€)",
  y= "Duration (seconds)",
  caption= "Note that balance can be negative!"
  )
```
**Statistical Methods**

The statistical methods that could be used is finding the mean,median, linear regression equation, standard deviation, a histogram, a box plot, and a bar plot.

Using the mean and median of numerical variables like age, bank balance and duration of calls out of the people which subscribed to the term deposit to approximate what is the ideal numeric value for this variables. In addition, a histogram, box plot or bar plot may be used to summarize discrete or continuous data that are measured on an interval scale like the relationship between how age and marital status affect the costumers decision.
