---
title: "Project Proposal"
author: "Conquerors"
date: "`r Sys.Date()`"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(readr)
```

## 1. Introduction

Fundamental Question: Which variables (or combinations of these) are the most important indicators when determining whether an individual will subscribe to a term deposit?

Data:
Where it came from?
How it was collected?
What are the cases?
What are the variables

The dataset "Banking Dataset - Marketing Targets" by Prakhar Rathi contains data  from a direct marketing campaign by a Portuguese Banking Institution. Clients were contacted by phone calls in order to collect the data.There are 45,211 cases with 17 variables;labelled: age, job, marital, education, default, balance, housing, loan, contact, day, month, duration, campaign, pdays, previous, poutcome, y.

## 2. Data

```{r import-data}

banking <- read_delim("/cloud/project/data/Banking Dataset.csv",
            delim = ";", escape_double = FALSE, trim_ws = TRUE)

glimpse(banking)

```


## 3. Data analysis plan

The outcome of this data(Y) is whether or not the client has subscribed to the term deposit the bank is offering. The predictor(X) variables are all the other variables in the dataset excluding Y which is the outcome variable. Our question will be answered by determining which of these variables are better predictors for this outcome.

We are not using any comparison groups because our data analysis research question is not based on experiment testing but rather on analyzing causation between different sets of variables. 




