---
title: "Project Proposal"
author: "Conquerors"
date: "`r Sys.Date()`"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(readr)
```

## 1. Introduction

**Fundamental Question:** Which variables (or combinations of these) are the most important indicators when determining whether an individual will subscribe to a term deposit?

**Data:**

The data set "Banking Dataset - Marketing Targets" by Prakhar Rathi contains data derived from *S. Moro, P. Cortez and P. Rita.-A Data-Driven Approach to Predict the Success of Bank Telemarketing*. The original data collection comes from the 2008-2013 records of a Portuguese Banking Institution and their success in convincing clients to subscribe to term deposits. 

**How was it collected?**

The data was collected directly from the bank's records through a semi-outomatic feature selection and DM models.

**What are the cases?**

There are 45,211 cases with 17 variables

**What are the variables?**

The variables are labelled: age, job, marital, education, default, balance, housing, loan, contact, day, month, duration, campaign, pdays, previous, poutcome, y (*Check README file in data folder for further description*).

**Original use of data:**

This data set was originally created to make a prediction model through machine learning that could determine whether newly-contacted clients would  subscribe to term deposits.

## 2. Data

```{r import-data}

banking <- read_delim("/cloud/project/data/Banking Dataset.csv",
            delim = ";", escape_double = FALSE, trim_ws = TRUE)

glimpse(banking)

```


## 3. Data analysis plan

The outcome of this data (Y) is whether or not the client has subscribed to the term deposit the bank is offering. The predictor(X) variables are all the other variables in the data set excluding Y which is the outcome variable. Our question will be answered by determining which of these variables are better predictors for this outcome.

We are not using any comparison groups because our data analysis research question is not based on experiment testing but rather on analyzing correlation and causation between different sets of variables that have all been pre-recorded.

**Preliminary Data Analysis:**

This first metric is used to observe the overall success of the bank marketing campaign.
```{r campaign_success }
banking %>%
  mutate(y=fct_recode(y, Subscribed= "yes", 
        `Not Subscribed` = "no")) %>%
ggplot(aes(y = y,fill= y)) +
  geom_bar() +
  guides(fill = "none") +
  scale_fill_manual(values = c("Subscribed"="#3b9e37", 
                              "Not Subscribed"="#d91a1a")) +
   labs(
    x = NULL,
    y = NULL,
    title = "Number of clients that subscribed to a term deposit",
  )
```

Could the client's jobs have an impact on whether they subscribe to term deposits?
```{r job_impact}
banking %>%
mutate(
  job= fct_recode(job, Administrative = "admin.",
                  Management = "management", 
                  Entrepreneur= "entrepreneur",
                  `Blue Collar` = "blue-collar", 
                  Housemaid = "housemaid", 
                  Technician = "technician" , 
                  Services = "services", 
                  Student = "student" , 
                  `Self Employed`= "self-employed", 
                  Unemployed = "unemployed", 
                  Unknown= "unknown", 
                  Retred = "retired" ),
  y=fct_recode(y, Subscribed= "yes", 
               `Not Subscribed` = "no")) %>%
ggplot(aes(y = y,fill= y)) +
  geom_bar() +
  guides(fill = "none") +
  scale_fill_manual(values = c("Subscribed"="#3b9e37", 
                               "Not Subscribed"="#d91a1a")) +
  facet_wrap(.~job, scales = "free_x") +
  labs(
    x = NULL,
    y = NULL,
    title = "Number of clients that subscribed to a term deposit",
    subtitle= "Faceted by jobs"
  )
```

Comparing two continuous variables such as Bank Balance and Duration of Call could help us determine whether the bank's marketing campaign placed more emphasis on clients with very large balances or negative ones (clients in need or with dept). Perhaps more effort was given to these groups of clients?

```{r balance_vs_duration}
banking %>%
  group_by(contact) %>%
  summarize(balance,duration) %>%
  ggplot(aes(x=balance,y=duration,color= contact)) +
  geom_smooth() +
  guides(color = "none") +
  facet_wrap(~contact,nrow = 3, scales = "free_x") +
labs(
  title= "Relationship between balance and duration of call",
  x= "Average Yearly Bank Balance (€)",
  y= "Duration (seconds)",
  caption= "Note that balance can be negative!"
  )
```

**Statistical Methods**

Some of the statistical methods that could be used in finding an answer to our question are mean,median,  standard deviation and regression analysis. Statistical visualization tools such as histograms, bar plot, dot plots, ridge plots, density plots and lines of best fit could also be used.

Using the mean and median of numerical variables like age, bank balance and duration of calls out of the people which subscribed to the term deposit to approximate what is the ideal numeric value for this variables. In addition, plots and graphs may be used to visualize discrete or continuous data like the relationship between how age and marital status affect the costumer's decision. Regression analysis can be used to estimate the relation between all other variables and our outcome variable.
