---
title: "Preliminary Visualizations"
output: github_document
---

```{r load-packages, include = FALSE}
library(rmarkdown)
library(tidyverse)
library(tidymodels)
library(knitr)
library(revealjs)
```


```{r read_csv}
banking_train<- read_delim("/cloud/project/data/Banking Dataset.csv",
            delim = ";", escape_double = FALSE, trim_ws = TRUE)

```

```{r 17 graph grid}
#variableGraphs<-function(df,name){
 # variable<- banking_test[ , name]
   #variable<- banking_test[ , name] %>%
banking_train%>%
  ggplot(aes(x=job,y=y))+
  geom_jitter()
banking_train%>%
  ggplot(aes(x=age,y=y))+
  geom_jitter()
banking_train%>%
  ggplot(aes(x=marital,y=y))+
  geom_jitter()
banking_train%>%
  ggplot(aes(x=education,y=y))+
  geom_jitter()
banking_train%>%
  ggplot(aes(x=default,y=y))+
  geom_jitter()
banking_train%>%
  ggplot(aes(x=balance,y=y))+
  geom_jitter()
banking_train%>%
  ggplot(aes(x=housing,y=y))+
  geom_jitter()
banking_train%>%
  ggplot(aes(x=loan,y=y))+
  geom_jitter()
banking_train%>%
  ggplot(aes(x=contact,y=y))+
  geom_jitter()
banking_train%>%
  ggplot(aes(x=day,y=y))+
  geom_jitter()
banking_train%>%
  ggplot(aes(x=month,y=y))+
  geom_jitter()
banking_train%>%
  ggplot(aes(x=duration,y=y))+
  geom_jitter()
banking_train%>%
  ggplot(aes(x=campaign,y=y))+
  geom_jitter()
banking_train%>%
  ggplot(aes(x=pdays,y=y))+
  geom_jitter()
banking_train%>%
  ggplot(aes(x=previous,y=y))+
  geom_jitter()
banking_train%>%
  ggplot(aes(x=poutcome,y=y))+
  geom_jitter()
```

```{r  graph grid}
banking_train%>%
  ggplot(aes(y=age,color=y))+
  geom_bar()
banking_train%>%
  ggplot(aes(y=job,color=y))+
  geom_bar()
banking_train%>%
  ggplot(aes(y=marital,color=y))+
  geom_bar()
banking_train%>%
  ggplot(aes(y=education,color=y))+
  geom_bar()
banking_train%>%
  ggplot(aes(y=default,color=y))+
  geom_bar()
banking_train%>%
  ggplot(aes(y=balance,color=y))+
  geom_bar()
banking_train%>%
  ggplot(aes(y=housing,color=y))+
  geom_bar()
banking_train%>%
  ggplot(aes(y=loan,color=y))+
  geom_bar()
banking_train%>%
  ggplot(aes(y=contact,color=y))+
  geom_bar()
banking_train%>%
  ggplot(aes(y=day,color=y))+
  geom_bar()
banking_train%>%
  ggplot(aes(y=month,color=y))+
  geom_bar()
banking_train%>%
  ggplot(aes(y=duration,color=y))+
  geom_bar()
banking_train%>%
  ggplot(aes(y=campaign,color=y))+
  geom_bar()
banking_train%>%
  ggplot(aes(y=pdays,color=y))+
  geom_bar()
banking_train%>%
  ggplot(aes(y=previous,color=y))+
  geom_bar()
banking_train%>%
  ggplot(aes(y=poutcome,color=y))+
  geom_bar()

#variableGraphs(df=banking_test, name=c("job"))